\section{Rules of Assessment}
    Refer to the exam regulations in the Faculty of Engineering Built
    Environment and Information Technology yearbook
    (\url{http://www.up.ac.za/en/yearbooks/faculties}).

    \noindent
    To pass the subject a student must:
    \begin{itemize}
        \item Obtain a final mark of at least 50\%; {\bf and}
        \item Obtain a subminimum of 40\% for the semester mark; {\bf and}
        \item Obtain a subminimum of 40\% for the final examination
    \end{itemize}

    \subsection{Determination of Final Mark}
        The final mark is compiled as follows:
        \begin{itemize}
            \item Semester mark: 50\%
            \item Final exam mark: 50\% (3-hour exam), closed-book behind a
                computer
        \end{itemize}

    \subsection{Determination of Semester Mark}
        The semester mark will be determined as shown in the table below:
        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|p{10cm}|c|l|l|}
               \hline
               {\bf Evaluation Method} & {\bf No. of} & {\bf Total} \\
               \hline
               Semester tests (written, closed book behind a computer)
               & 2 & {\bf 80\%} \\ \hline
               Individual project
               & 1 & {\bf 10\%} \\ \hline
               Group project
               & 1 & {\bf 10\%} \\ \hline
               \multicolumn{2}{|l|}{{\bf Total}} & {\bf 100\%} \\
               \hline
             \end{tabular}
             \caption{Determination of Semester Mark}
            \end{center}
        \end{table}

    \subsubsection{Semester Tests}
        Two tests will be written during the semester, in the weeks 10
        to 17 March 2018 and 5 to 12 May 2018. The duration of each test will
        be 90 minutes. Syllabi of the tests will be announced during the
        lecture week preceding the test week. Both tests will be closed-book.
        The tests will be written in the computer labs where the students will
        have access to Python and LibreOffice.

        Additional test instructions will be announced during the lecture
        week preceding the test week and uploaded to {\it ClickUP}.

        Memoranda on the scheduled tests will be made available in electronic
        format on {\it ClickUP} and will not be discussed during lectures. You
        may make use of the discussion board on {\it ClickUP} should you have a
        specific question regarding a problem given in the semester tests.

    \subsubsection{Weekly Assignments}
        Weekly assignments will be posted to \textit{ClickUP} for hand-in by a
        specific date. Weekly assignments are provided as a means to further
        develop the students understanding and knowledge of the topics covered
        in lectures. Weekly assignments will not count towards the calculation
        of the semester mark, but will set the student in good stead towards
        the preparation for tests and exams.

        Weekly these assignments will be graded electronically and feedback
        provided to the students. Note that the electronic grading
        system can only award 0\% or 100\% (binary grading) for each question.
        It is also extremely important that you follow the hand-in instructions
        on requested filenames, object names, function names, etc. otherwise
        the grading system (when confused) will award 0\%.

    \subsubsection{Individual Project}
        Detailed information regarding the individual project will be posted to
        {\it ClickUP} at a later stage.

        \textbf{Note:} As the name suggests the individual project must be
        solved and programmed independently. All electronically submitted
        material is easily checked for plagiarism, which will not be tolerated.
        Refer to the Departmental Study Guide (see section
        \ref{sec:dep_study_guide}) for more information on plagiarism.

    \subsubsection{Group Project}
        The group semester project is an opportunity for students to work
        together as a group to solve a common problem.

        A ``Group Project Guide'', detailing the project and requirements,
        will be added to {\it ClickUP} at a later stage.

        \textbf{Note:} All electronically submitted material is easily checked
        for plagiarism, which will not be tolerated. Refer to the Departmental
        Study Guide (see section \ref{sec:dep_study_guide}) for more
        information on plagiarism.

    \subsection{Appeals and queries on marks}
        In accordance with the Departmental Study Guide, students have a 14
        day period within which they can appeal for an adjustment of marks
        due to errors in grading or other interpretation related matters.
        Any adjustments will only be made at the discretion of the lecturer.
        After this 14 day period no marks will be altered. Refer to the
        Departmental Study Guide (see section \ref{sec:dep_study_guide})
        for more information.

        \subsubsection{Appeal process for semester tests}
            \begin{enumerate}
                \item Download the memorandum, feedback, and query documents
                    from {\it ClickUP}.
                \item Go through your test paper carefully along with the
                    memorandum and feedback documents.
                \item Fill out the query form, describing your appeal or query,
                    and attach it to your question paper.
                \item Hand your question paper in to the lecturer at the end of
                    the lecture within the 14 day window period.
            \end{enumerate}

            \textbf{No paper will be accepted without a query form attached.}
            Only at the end of the 14 days window period (once all query forms
            have been received) will the lecturer re-grade / re-evaluate your
            paper.

