\section{Rules of Assessment}
    Refer to the exam regulations in the Yearbooks of the Faculty of Engineering,
    Built Environment and Information Technology.

    To pass the subject a student must:
    \begin{itemize}
        \item Obtain a final mark of at least 50\%; {\bf and}
        \item Obtain a subminimum of 40\% for the semester mark; {\bf and}
        \item Obtain a subminimum of 40\% for the final examination
    \end{itemize}

    \subsection{Determination of Final Mark}
        The final mark is compiled as follows:
        \begin{itemize}
            \item Semester mark: 50\%
            \item Final Exam mark: 50\% (3-hour exam), closed-book behind a computer
        \end{itemize}

    \subsection{Determination of Semester Mark}
        The semester mark will be determined as shown in the table below:
        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|p{6cm}|c|l|l|}
               \hline
               {\bf Evaluation Method} & {\bf No. of} &
               {\bf Contribution of ea.} & {\bf Total} \\
               \hline
               Semester tests (written, closed book behind a computer)
               & 2 & 40\% & {\bf 80\%} \\ \hline
               Semester Project
               & 1 & 10\% & {\bf 10\%} \\ \hline
               Tutorial Assignments
               & \multicolumn{2}{|c|}{All} & {\bf 10\%} \\
               \hline
               \multicolumn{3}{|l|}{{\bf Total}} & {\bf 100\%} \\
               \hline
             \end{tabular}
             \caption{Determination of Semester Mark}
            \end{center}
        \end{table}

    \subsection{Semester Tests}
        Two tests will be written during the semester, in the weeks 8 to 15
        March 2014 and 5 to 10 May 2014. The duration of each test will be
        90 minutes. Syllabi of the tests will be announced during the lecture
        week preceding the test week. Both tests will be closed-book. The
        tests will be written in the computer labs where the students will
        have access to Python.

        Additional test instructions will be announced during the lecture
        week preceding the test week and uploaded to {\it ClickUP}.

        Memoranda on the scheduled tests will be made available in electronic
        format on {\it ClickUP} and will not be discussed during lectures. You may
        make use of the discussion board on {\it ClickUP} should you have a specific
        question regarding a problem given in the semester tests.

    \subsection{Tutorials}
        Tutorial assignment questions indicated for hand-in need to be
        uploaded onto ClickUP before by due date. \textbf{Please note that
        these assignments will be graded electronically with each
        question receiving a grade of 0\% or 100\% (binary grading). It
        is therefore extremely important that you follow the hand-in
        instructions on requested filenames, object names and function
        names. Failure to do so will result in a zero grade for the
        question.}

        \textbf{Note:} Tutorial assignments must be solved and
        programmed independently. All electronically submitted
        material is easily checked for plagiarism, which will not be
        tolerated. Refer to the Departmental Study Guide (see section
        \ref{sec:dep_study_guide}) for more information on plagiarism.

    \subsection{Appeals and queries on marks}
        In accordance with the Departmental Study Guide, students have a 14
        day period within which they can appeal for an adjustment of marks
        due to errors in grading or other interpretation related matters.
        Any adjustments will only be made at the discretion of the lecturer.
        After this 14 day period no marks will be altered. Refer to the
        Departmental Study Guide (see section \ref{sec:dep_study_guide})
        for more information.

        \subsubsection{Appeal Process}
            \begin{enumerate}
                \item Download the memorandum, feedback and query documents
                    from {\it ClickUP}.
                \item Go through your test paper carefully along with the
                    memorandum and feedback documents.
                \item Fill out the query form, describing your appeal or query,
                    and attach it to your question paper.
                \item Hand your question paper in to the lecturer at the end of
                    the lecture within the 14 day window period.
            \end{enumerate}

            \textbf{No paper will be accepted without a query form attached.}
            Only at the end of the 14 days window period (once all query forms
            have been received) will the lecturer re-grade / re-evaluate your
            paper.
