\section{Lecturers and Consulting Hours}
    \subsection{Lecturers}
        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|l|l|c|l|}
                 \hline
                 {\bf Lecturer} & {\bf Office} & {\bf Telephone No.} & {\bf Email} \\
                 \hline
                 Mr Logan Page &
                 Eng III 6--93 &
                 (012) 420 6891 &
                 \href{mailto:logan.page@up.ac.za}{logan.page@up.ac.za} \\
                 %
                 Mr Stephan Roux &
                 Eng III 6--91 &
                 (012) 420-2935 &
                 \href{mailto:stephan.roux@up.ac.za}{stephan.roux@up.ac.za} \\
                 \hline
             \end{tabular}
            \end{center}
        \end{table}

        For e-mail correspondence, please use the keyword
        \textbf{MPR213} in the e-mail subject specification.

    \subsection{Teaching Assistants}
        The contact details and consulting hours for the teaching assistants
        will be added to {\it ClickUP} as soon as the teaching assistants have
        been allocated.

    \subsection{Consulting Hours}
        Consultation hours of the lecturers and teaching assistants will be
        announced at the start of the semester. These hours will also be
        displayed on their office doors and on {\it ClickUP}. These hours
        indicate when the lecturers and teaching assistants are on campus and
        available for consultation. Students are requested to please make an
        appointment so as to ensure that the lecturers and teaching assistants
        are in their offices.

        Students are welcome to make special arrangements to see the
        lecturers at times outside of their consulting hours if
        necessary. It is important not to wait until just before a
        test or exam to clarify any problems. There will be no
        extraordinary consulting hours during test and exam time.

        Students are also welcome to make use of the discussion board
        on the new {\it ClickUP} system. This will allow lecturers,
        teaching assistants and fellow students to answer any queries
        regarding programming concepts, exercise problems, etc. during
        their free time.
