\section{Study Components}
    \subsection{Purpose of the module}
        {\bf Advanced spreadsheet applications:} \\
        Named ranges, linear algebra,
        solution of systems of equations, regression, interpolation,
        optimization and table manipulation. \\ \\
        {\bf Basic structured programming:} \\
        Looping, branching, subroutines, iteration, reading and writing data
        files. Development, coding and debugging of simple programs in a high
        level programming language. Programming principles are illustrated via
        mathematical concepts such as limits, differentiation, integration
        and linear algebra. Structured programming by making use of functions
        and available packages. Basic graphical output (plotting) is also
        covered.

    \subsection{Module Structure}
        The structure of this module is shown in table \ref{tab:study_comp}.
        The total module hours (notational hours) include the contact time,
        as well as the estimated time to be allocated for self-study,
        preparation of assignments, tests and the examination. The mode of
        instruction is via lectures, tutorial class and assignment.

        \begin{longtable}{|p{1.4cm}|p{8.4cm}|p{2.2cm}|p{1.8cm}|}
             \hline
             \multicolumn{1}{|p{1.4cm}|}{\textbf{Theme No.}} & %
             \multicolumn{1}{p{8.4cm}|}{\textbf{Topic}} &  %
             \multicolumn{1}{p{2.2cm}|}{\textbf{Notational Hours}} & %
             \multicolumn{1}{p{1.8cm}|}{\textbf{Contact Sessions}} \\
             \hline \endfirsthead

             \multicolumn{4}{l}%
             {\textbf{...continued from previous page}} \\
             \hline
             \multicolumn{1}{|p{1.4cm}|}{\textbf{Theme No.}} & %
             \multicolumn{1}{p{8.4cm}|}{\textbf{Topic}} &  %
             \multicolumn{1}{p{2.2cm}|}{\textbf{Notational Hours}} & %
             \multicolumn{1}{p{1.8cm}|}{\textbf{Contact Sessions}} \\
             \hline

             \hline \endhead
             \hline \endfoot
             \endlastfoot

             1  & Introduction to Computers and Programming  &    &    \\
             \hline
             2  & Basic Programming                          & 12 & 4  \\
                & \qquad Using Python as a Calculator        &    &    \\
                & \qquad Names, Objects and Assignment       &    &    \\
                & \qquad Swapping Objects                    &    &    \\
                & \qquad Basic List Generation               &    &    \\
             \hline
             3  & Control Statements                         & 56 & 12 \\
                & \qquad Iterator-Based Looping (For Loop)   &    &    \\
                & \qquad Conditional Looping (While Loop)    &    &    \\
                & \qquad Branching (If, Elif, Else)          &    &    \\
             \hline
             4  & Iterators                                  &  8 & 2  \\
                & \qquad Iterating Through Lists             &    &    \\
                & \qquad Growing Lists + Loops               &    &    \\
                & \qquad Other Iterators                     &    &    \\
             \hline
             5  & Structured Programming (Functions)         &  8 & 2  \\
                & \qquad User-defined Functions              &    &    \\
                & \qquad Code Structure (modules vs scripts) &    &    \\
                & \qquad Local Namespace                     &    &    \\
             \hline
             6  & Nested Structures                          & 20 & 4  \\
                & \qquad Nested Control Statements           &    &    \\
                & \qquad Nested Iterators                    &    &    \\
                & \qquad Use of Functions (Simplification)   &    &    \\
             \hline
             7  & Plotting and Graphs                        & 16 & 4  \\
                & \qquad Numpy Objects and Functions         &    &    \\
                & \qquad 2D Graphs                           &    &    \\
                & \qquad Graph Annotation                    &    &    \\
                & \qquad 3D Graphs                           &    &    \\
             \hline
             8  & Data Handling                              &  6 & 2  \\
                & \qquad Reading and Writing Data            &    &    \\
                & \qquad Data Sharing between Application    &    &    \\
             \hline
             9  & High Level Programming                     &  6 & 2  \\
                & \qquad Additional Modules                  &    &    \\
                & \qquad Advanced Build-In Functions         &    &    \\
             \hline
             10 & Graphical User Interfaces (GUI's)          & 16 & 4  \\
                & \qquad TKinter Module                      &    &    \\
                & \qquad Forms and Form Objects              &    &    \\
                & \qquad Mouse / Keyboard Events             &    &    \\
             \hline
             11 & Spreadsheets                               & 32 & 8  \\
                & \qquad Formulas and Calculations           &    &    \\
                & \qquad Spreadsheet Detective               &    &    \\
                & \qquad Plotting and Graphs                 &    &    \\
                & \qquad Linear Programming                  &    &    \\
                & \qquad Non-Linear Solver problems          &    &    \\
                & \qquad Data Pilot                          &    &    \\
                & \qquad What-if Scenarios                   &    &    \\
                & \qquad Visual Formatting                   &    &    \\
             \hline
                & {\bf TOTAL}                                &180 &44  \\
             \hline

             \caption[Module Structure]{Module Structure} \label{tab:study_comp} \\
        \end{longtable}

    \subsection{Lecture Plan}
        This outlines the lecture plan for the semester. Students should use
        this plan to make sure that they do not fall behind the class
        lectures and/or tutorials. There are a total of 48 lectures and 12
        tutorial sessions over the 13 weeks of the semester.

        Table \ref{tab:lec_plan} lists which study themes will be covered
        in which weeks of the semester. Each week has a corresponding tutorial
        which should be completed during the specific week in the tutorial
        sessions.

        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|l|l|l|l|l|}
                 \hline
                 {\bf Week} & {\bf Lectures} & {\bf Dates} & %
                 {\bf Study Theme} & {\bf Tutorial} \\
                 \hline
                 1  & 4     &  3 –-  7 Feb     & 1, 2  & None \\
                 2  & 4     & 10 –- 14 Feb     & 3     & T1 \\
                 3  & 4     & 17 –- 21 Feb     & 3     & T2 \\
                 4  & 4     & 24 –- 28 Feb     & 3     & T3 \\
                 5  & 4     &  3 –-  7 Mar     & 4, 5  & T4 \\
                    &       & == TESTWEEK 1 == &       & \\
                 6  & 4     & 17 -- 20 Mar     & 6     & T5 \\
                 7  & 4     & 24 -- 28 Mar     & 7     & T6 \\
                    &       & ==== RECESS ==== &       & \\
                 8  & 4     &  7 -- 11 Apr     & 11    & T7 \\
                 9  & 2 / 4 & 14 -- 17 Apr     & 11    & T8 \\
                 10 & 2     & 22 -- 25 Apr     & 11    & T9 \\
                    &       & == TESTWEEK 2 == &       & \\
                 11 & 4     & 12 -- 16 May     & 8, 9  & T10 \\
                 12 & 4     & 19 -- 23 May     & 10    & T11 \\
                 13 & 4     & 26 -- 29 May     & Recap & T12 \\
                    &       & ===== EXAM ===== &       & \\
                 \hline
             \end{tabular}
             \caption{Lecture Plan} \label{tab:lec_plan}
            \end{center}
        \end{table}

        Notational hours include contact time, as well as the estimated time
        necessary for preparation for tests and exams. Contact sessions indicate
        the regular lectures. The number of contact sessions per chapter is
        tentative. It may change depending on the progress during lectures.

        Please note that some subsections in a chapter of the textbook will not be
        covered during the lectures, whereas other subsections may be given as
        self-study. The lecturer will provide information about the sub-sections
        that will not be covered for test- and exam purposes.

        Selected exercise problems, from the study notes, will be covered during
        the tutorial sessions. The selected chapters and problems (from the study
        notes) that will be covered in each tutorial session will be added to
        Click-UP.

    \subsection{Fundamental Concepts}
        The following concepts need to be mastered in order to pass the course.
        If any of the following concepts are not mastered, the student will
        fail the course:
        \begin{itemize}
            \item Basic Objects (e.g. int vs float)
            \item Importing modules and proper usage
            \item For Loop (Proper usage and understanding when and why to use
                a for loop)
            \item Iterating through Lists and growing lists (single lists, not
                nested lists)
            \item While Loop (Proper usage, understanding termination
                conditions and understanding when and why to use a while loop)
            \item If Statements (Proper usage, understanding program flow and
                control and understanding when and why to use an if, elif or
                else statement)
            \item Functions (able to properly create a new function, understand
                how objects are parsed to and from functions, be able to
                properly use any created function)
            \item Plotting (be able to create a simple 2D plot with proper
                annotations)
        \end{itemize}

    \subsection{Study Theme Descriptions}
        \subsubsection{Theme 1: Introduction to Computers and Programming}
            The introduction allows the student to obtain a general overview.
            This section will not be explicitly tested. It is important to note
            that an understanding of computer architecture and flow diagrams
            will make the following sections more accessible.

        \subsubsection{Theme 2: Basic Programming}
            \paragraph{Using Python as a Calculator:}
                The student has to ensure that he/she is comfortable with the
                \emph{IPython Console} and \emph{Spyder} environments and must
                be able to use Python to do simple mathematical calculations.
                It is the student's responsibility to spend enough time using
                these environments throughout the semester.

            \paragraph{Names, Objects and Assignment:}
                The student has to be familiar with the guidelines in the class
                notes on names and objects e.g. objects are created in memory
                and a name is assigned to that object. The student must also
                be familiar with the memory model of Python. The student must
                also know the difference between the object types e.g. int,
                float, str, bool.

            \paragraph{Swapping Objects:}
                The student must be able to swap 2 objects without destroying
                the name assignment. The student also has to be familiar with
                the memory model on how objects or swapped and not over-written.

            \paragraph{Basic List Generation:}
                The student must be able to generate a simple list objects,
                both manually and by using the range function. The student also
                has to be familiar with the various list operators and
                functions.

        \subsubsection{Theme 3: Control Statements}
            \paragraph{For Loop:}
                The student has to be able to identify when and why to use
                for loop/s from a given problem statement. The student has to
                be familiar with Python's syntax and indentation and be able
                to implement for loop/s in a program to perform a given task.

            \paragraph{While Loop:}
                The student has to be able to identify when and why to use
                while loop/s from a given problem statement. The student has to
                be familiar with Python's syntax and indentation and be able
                to implement while loop/s in a program to perform a given task.
                The student also has to be able to determine the correct
                while loop termination conditions in order to perform a given
                task.

            \paragraph{Branching:}
                The student has to be able to identify the usage of branches
                (when and why to use an if, elif or else statement) from
                a problem statement. The student has to be familiar with
                Python's syntax and indentation and be able to implement
                branches in a program to perform a given task. The student
                needs to understand how each of the if, elif and else
                statements effects the program flow and control. The student
                also has to be able to determine the correct conditions in
                order to perform a given task.

        \subsubsection{Theme 4: Iterators}
            \paragraph{Iterating Through Lists:}
                The student has to understand the principles of lists, tuples and 
                dictionaries as well as the Python syntax thereof. The student must
                be able to identify and be able to implement lists, tuples and 
                dictionaries. The student must be able to rewrite an existing 
                computer program that uses variables such that it uses either
                lists, tuples or dictionaries.

        \subsubsection{Theme 5: Structured Programming}
            The student must be familiar with functions, subfunctions and code 
            structure. The student must be able to create functions with multiple 
            inputs and outputs as well as optional (keyword) inputs. The student 
            must be able to rewrite an existing computer program such that it makes
            use of functions and subfunctions. The student has to be familiar with 
            local variables and understand their scope within a function, 
            subfunction or module.

        \subsubsection{Theme 6: Plotting and Graphs}
            The student must be able to create 2D plots i.e. the student must be 
            familiar with different presentations of data, presenting multiple 
            graphs on the same figure, displaying grids, labelling of the axis, 
            naming of figures, using legends and scaling axis systems.
            The student must be able to create 3D figures. The student has to be 
            familiar with creating surface and mesh plots.

        \subsubsection{Theme 7: File Handling}
            The student must be familiar with reading and writing to and from 
            files, as well as the various file types in Python. The student must 
            be able to store the data in a given format. The student must also
            understand how to access different directories from within the Python
            program.

        \subsubsection{Theme 8: High Level Programming}
%             \paragraph{Error Handling:}
%                 
%                 
%             \paragraph{Advanced Programming:}
            
%             \paragraph{Additional Modules:}
                The student must be able to solve over and under determined linear
                systems of equations, non-linear systems of equations and systems 
                of linear differential equations using additional modules and 
                functions in Python. The student must be able to manipulate 
                polynomials, conduct optimization, integrate numerically, obtain
                descriptive statistical measures of data and interpolate numerical 
                data using using additional modules and functions in Python.
                
                The student must be able to navigate Python's documentation 
                as well as online documentation and be able to find, read and 
                understand the documentation of the required functions in order 
                to solve specific problems. The student should therefore be able
                to independently increase his/her knowledge of the Python
                programming language.

        \subsubsection{Theme 9: Spreadsheets}
            \paragraph{Formulas and Calculations:}
                The student must be able to solve problems using formulas. The
                student must be able to solve problems using functions that he/she
                are familiar with, as well as use the function wizard for unknown
                functions. The student must be able to name ranges of cells and use
                them in calculations.

                The student must be able to use filters to filter data and perform
                calculations on the filtered dataset. The student must be able to
                perform calculations on data that is split over multiple
                spreadsheets.

            \paragraph{Spreadsheet Detective:}
                The student must be able to use the spreadsheet detective to
                familiarise themselves with the dependencies in an unknown
                spreadsheet. The student must be able to switch between formula
                and value view.

            \paragraph{Plotting and Graphs:}
                The student must be able to create and customise charts. The
                student must be able to find trends in data.

            \paragraph{Linear Programming:}
                The student must be able to solve linear programming problems
                using LibreOffice Calc. The student must be able to solve
                problems with mixed integer, real and boolean variables. The
                student must be able to accommodate multiple constraints.

            \paragraph{Non-Linear Solver:}
                The student must be able to solve non-linear one dimensional
                problems using goal seek in LibreOffice Calc.

            \paragraph{Data Pilot:}
                The student must be able to extract relational data using the Data
                Pilot in LibreOffice Calc.

            \paragraph{What-if Scenarios:}
                The student must be able to perform what-if investigations using
                the scenario function in LibreOffice Calc.

            \paragraph{Visual Formatting:}
                The student must be able to improve the appearance of a worksheet
                by using colours, highlighting, borders and font properties. The
                student must be able to perform conditional formatting of cells.
        
            
        \subsubsection{Theme 10: HTML, Websites and the Internet}
            The student should understand that basic websites are just a 
            text file with special HTML tags. The student should be able to 
            modify existing html websites. Finally the student should know 
            how to do advanced searches on the internet for information.
        

        \subsubsection{Theme 11: Databases}
            The student should know and understand what a database is and when a 
            database is the correct data structure to store data. The student 
            should be able to create a database of information using a database 
            software package and should be able to create queries and reports 
            based on the data in the database.
