\section{Learning Activities}
    \subsection{Contact Time and Learning Hours}
        \begin{minipage}{0.4\linewidth}
            Number of lectures a week: \\
            Tutorial sessions a week:
        \end{minipage}
        \begin{minipage}{0.4\linewidth}
            4 lectures, 50 minutes per lecture \\
            1 session, 100 minutes per session
        \end{minipage}

        This module carries a weight of 18 credits, indicating that a student
        should spend an average of 180 hours to master the required skills 
        (including time spent preparing for tests and examinations). This means
        that you should devote an average of 12 hours of study time per week to
        this module. The scheduled contact time is approximately seven hours per
        week, which means that another five hours per week of own study time
        should be devoted to the module.
    
    \subsection{Lectures}
        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|l|c|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{1.5cm}|}
                 \hline
                 {\bf \#} & {\bf Time} & {\bf Mon.} & {\bf Tues.} & {\bf Wed.} &
                 {\bf Thurs.} & {\bf Fri.} \\
                 \hline
                 1  & 07:30--08:20 &  &  &  &  & \\ \hline
                 2  & 08:30--09:20 &  Ing III -- 1 (Afr)  &  & Ing III -- 6 (Afr) &  & \\ \hline
                 3  & 09:30--10:20 &  &  &  & Ing III -- 6 (Afr) & \\ \hline
                 4  & 10:30--11:20 &  &  &  &  & \\ \hline
                 5  & 11:30--12:20 &  &  &  & Thuto 1 -- 1 (Eng) & \\ \hline
                 6  & 12:30--13:20 &  &  &  & Thuto 1 -- 1 (Eng) & \\ \hline
                 7  & 13:30--14:20 &  &  &  &  & \\ \hline
                 8  & 14:30--15:20 &  &  &  &  & \\ \hline
                 9  & 15:30--16:20 &  & Thuto 1 -- 2 (Eng) &  &  & \\ \hline
                 10 & 16:30--17:20 &  & Thuto 1 -- 2 (Eng) &  &  & \\ \hline
                 11 & 17:30--18:20 &  & Ing III -- 6 (Afr) &  &  & \\
                 \hline
             \end{tabular}
             \caption{Lecture Time Table}
            \end{center}
        \end{table}
        
        Lecture attendance and participation in discussions are compulsory. 
        Since the contents of each lecture follow on those of previous lectures, 
        it is in the students’ own interest to study the material covered on a regular
        basis and not to miss a lecture. However, should a student not be able to
        attend a certain lecture for whatever reason, the onus is on him / her to
        obtain the study material and catch up on the work. No individual lectures
        will be presented. Previous material will rarely be repeated in a following 
        lecture.
        
        Students are expected to prepare for lectures. Since a large volume of work
        needs to be covered, it is not possible to lecture every aspect in the 
        finest detail. Students should therefore read the textbooks thoroughly 
        and already know beforehand what the next lecture is about in order to 
        identify anything that is unclear. The lecturer may also assign some 
        sections of the study notes and lecture notes / handouts for self-study. 
        These sections will be part of the syllabus, but will not be discussed 
        in the class.
        
        Dr Wilke will present the lectures in Afrikaans and Mr Page will present
        the lectures in English (according to the time table shown above). The
        lectures are split as per the time table above. Please refer to Click-Up 
        for any time table updates.
        
    \subsection{Homework Problems}
        The lecturer may provide analytical problems to enhance the students’
        independent skills to formulate the problem physics and analyse the 
        applications of the theory. Students should work out the problems in
        their own time. The problems do not have to be submitted as they will
        not be evaluated. No solutions will be provided for these homework 
        problems.
        
        It will be to the benefit of the student to complete these problems as
        similar forms of the problems may be asked in the tests or exam.
        You may make use of the discussion board on Click-UP should you have a 
        specific question regarding a given homework problem.
    
    \subsection{Tutorials}
        \begin{table}[!h]
            \begin{center}
             \begin{tabular}{|l|l|l|l|}
                 \hline
                 {\bf Discipline} & {\bf Day} & {\bf Time} & {\bf Venue} \\
                 \hline
                 b3 B2     & Thurs. & 14:30-16:20 & NWII Lab 1,2 \\
                 c3s3 C2   & Mon.   & 15:30-17:20 & NWII Lab 2,3,4 \\
                 m3 M2     & Fri.   & 13:30-15:20 & NWII Lab 1,2 \\
                 n3p3 N2P2 & Wed.   & 11:30-13:20 & NWII Lab 1,2 \\
                 M2        & Tues.  & 07:30-09:20 & NWII Lab 2,3,4 \\
                 S3        & Mon.   & 11:30-13:20 & NWII Lab 1,2,3,4 \\
                 \hline
             \end{tabular}
             \caption{Tutorial Time Table}
            \end{center}
        \end{table}
        
        Tutorial sessions will be used to further develop the students 
        understanding and knowledge of the topics covered in lectures by
        solving numerous engineering and mathematical problems with the 
        tools introduced in this module.
        
        Tutorial session attendance and participation in discussions are compulsory. 
        Since the contents of each tutorial session follows on those of previous 
        tutorial session, it is in the students’ own interest to study the material 
        covered on a regular basis and not to miss a tutorial session. 

